Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-06-11 Notebook LaTEX/R-WAPG/presentation.tex
>w<, changes

% SLIDE INFORMATION ============================================================
\author{Hongda Li, Wang Xianfu}
\title[Thesis Proposal Talk]{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date{\today}
\subject{Nesterov's acceleration and its applications}

@@

            If $F$ is convex and has $L$ Lipschitz smooth gradient and minimizer $x^+$ exists. 

@@

                \item a convergence rate of $\mathcal O(1/k^2)$ of $(F(x_k) - F(x^+))_{k \ge 1}$;

@@

            Disregarding the definition of $(t_k)_{k \ge 0}$ for now. 

@@

                \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ in the weakest possible way to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists. 

@@

                \item We demonstrate that the R-WAPG framework can be represented is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature. 

@@

            We can show Nesterov's type accelerated proximal gradient algorithm (similar to what's show in prior but with $g \equiv 0$) which generates $(F(x_k) - F^+)_{k\ge 1}$ has an upper bound of: 

@@

                We all the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 

@@

\section{Our paper is on arxiv and references}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=17em]{assets/paper-qrcode.png}
        \end{figure}
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}

>>>>

% SLIDE INFORMATION ============================================================
\author[Hongda Li]{Hongda Li\\ \vspace{1cm} \tiny{Joint work with Xianfu Wang}}
\title[Thesis Proposal Talk]{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date{\today}
\subject{Nesterov's acceleration and its applications}

@@

            If $F$ is convex and has $L$ Lipschitz smooth gradient and a minimizer $x^+$ exists. 

@@

                \item a convergence rate of $\mathcal O(1/k^2)$ for $(F(x_k) - F(x^+))_{k \ge 1}$;

@@

@@

                \item We relaxed the traditional choices of the sequence $(\theta_k)_{k \ge 1}$ to full extend to show that an upper bound for the sequence $(F(x_k) - F^+)_{k \ge 1}$ exists. 

@@

                \item We demonstrate that the R-WAPG framework is equivalent to various representations of the Nesterov's type accelerated proximal gradient methods with Euclidean geometry in the literature. 

@@

            We can show Nesterov's type accelerated proximal gradient algorithm (or equivalently, FISTA with $g \equiv 0$) generates $(F(x_k) - F^+)_{k\ge 1}$ has an upper bound of: 

@@

                We call the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ the R-WAPG sequences. 

@@

\section{Our paper is on arxiv and references}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}
